---
title: "SensorThings API Demo"
author: 
  - Kyle Onda^[Internet of Water, kyle.onda@duke.edu]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 8
    fig_height: 8
    theme: readable
  
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


```
## SensorThings: Interoperability for georeferenced observation data

You can do great things with SensorThings API. Any instance of SensorThings API can be interacted with using the same functions. For example, I have written a small R package (available at [https://github.com/internetofwater/sta4R](https://github.com/internetofwater/sta4R) that provides commands that can be applied to any SensorThings API endpoint. For example, a function called `sta_mapview()` that takes as an input the URL of any SensorThings API endpoint, and turns it into an interactive leaflet map. Below, I show how this function can be used to quickly create a map visualization of three separate SensorThings API endpoints (the one offered by NMBGMR, a proxy of the USGS National Groundwater Monitoring Network, and a proxy of the NMED instance of SDWIS/State)

```{r setup, results='asis'}
#devtools::install_github("internetofwater/sta4R")
library("sta4R")

api_nmbgmr <- "https://st.newmexicowaterdata.org/FROST-Server/v1.1"
api_usgs <- "https://sta-demo.internetofwater.dev/api/v1.1"
api_nmed <- "https://e-enterprise-test.apigee.net/sdwis/sta/v1.0"

plot <- sta_mapview(api_usgs,col.regions="green", layer.name="National Groundwater Monitoring Network") + 
  sta_mapview(api_nmbgmr, col.regions="red", layer.name="New Mexico Bureau of Geology and Mineral Resources") + 
  sta_mapview(api_nmed, col.regions="orange", layer.name="NMED SDWIS", cex=3)

leaflet::setView(plot@map,-106,34.6, zoom=7)
```



